Put Title here

### 2018-11-27 General WLD combinatorics.tex
just some little things

@@

\begin{lem}\label{lem sian 1}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
  %Then exactly one of the following two things occurs.
  %\begin{enumerate}
  %  \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
  %  \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
  %    \begin{enumerate}
  %      \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
  %      \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  %      \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
  %    \end{enumerate}
  %\end{enumerate}
\end{lem}

@@

\begin{rmk}
In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian 1} substantially simplifies.  By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$, so the first item of Lemma~\ref{lem sian 1} cannot occur at all.  Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.  So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
\end{rmk}

@@

\note{This is a mess for now; protecting sets commented out, and 1.5 versions of the induction copied in by not yet edited}

This is the lemma from the email with the proof copied from the email.
\begin{lem}\label{lem last vert}
  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.  Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
\end{lem}

@@

\textbf{case I}:  Suppose $p$ has one end on $(i-1, i)$.  Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap \interval{i+1}{b-1} = I_{i} \cap \interval{i+1}{b-1}$.  Furthermore, by Lemma~\ref{lem susama}, in building $I_{i+1}$, it must be that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.    Consequently, in building $I_{i+1}$, when at vertex $b$ no propagator still remaining is before $p$.  This is also true in building $I_i$ when at $b$ since the same propagators have been taken beforehand.  Additionally $k\geq_i b+1$.

@@

The first lemma is Lemma~\ref{lem susama} and I moved it up to a previous section.

@@

The third lemma is Sian's result.

\begin{lem}\label{lem sian}
  Let $D$ be a WLD with all vertices covered by at least two propagators.  Then There exist two propagators in $D$ with the following properties.
  \begin{itemize}
  \item The first propagator goes from the edge $i$, $i+1$ to the edge $i+2$, $i+3$.
  \item The second propagator goes from the edge $i+2$, $i+3$ to the edge $i+4$, $i+5$
  \item No other propagator is on the edge $i+2$, $i+3$.
  \end{itemize}
\end{lem}

Actually the result I need is not exactly Sian's result and what I will actually use is her proof.  Thus I will use notation and definitions (including length of a propagator and the specific $p_i$ and $q_i$ construction from the proof) from her note without further discussion.  The result I will actually use will be that in place of the hypothesis that $D$ has all vertices covered by at least two propagators I have that all vertices are covered by at least 1 propagator and there are no propagators of length 3.

@@

  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{lem susama}.  Thus $n-3\not\in I_1^{C}$ and so in building the Gra\ss mann necklace when we get to vertex $n-3$ any other covering propagators of $C$ have already been taken and so we can now take $p$.  Therefore $I_1^{D}= I_1^{C}\cup \{n-3\}$.

@@

  The remaining case is when $n-1,n-2\in I_{n-2}^{C}$ for the construction of $I_{n-2}^{D}$.  We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.  In the construction of $I_{n-2}^{D}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{C}$.  Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{C}$.  Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.  Thus we are proceeding like $I_{n}^{C}$ but without propagator $q$.  Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{C}$.  By Lemma~\ref{lem susama} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.  Therefore $I_{n-2}^{D} = (I_{n}^{C} - \{n-5\}) \cup \{n-1, n-2\}$.  This covers all cases and hence completes the proof.
\end{proof}

@@

  Also by Lemma~\ref{lem I} $I_{n-1}^{D} = I_n^{C} \cup \{n-1\}$.  Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{lem susama}.  Similarly $n-1, n-2\not\in I_n^{C}$.  Thus the paths putting the plusses in from $I_n^{C}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $D$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{D}$ contributes.  That is, we get all the plusses from $I_{n}^{C}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
\end{proof}

@@

\begin{proof}
  If $n-2\not\in I_{n-2}^{C}$ then $I_{n-1}^{C}=I_{n-2}^{C}$ and by Lemma~\ref{lem I} $I_{n-2}^{D} = I_{n-1}^{C} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{lem susama}.  Therefore the paths for $I_{n-2}^{D}$ are the paths for $I_{n-1}^{C}$ along with the $n-3\rightarrow n-2$ path.  This gives the statement of the lemma.

@@

\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.  
%Call the propagators which appear before $p$ is closed the propagators inside $p$. \note{It might be nice to have general language for this inside/outside idea.  What do you think.}

@@

\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.  Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$. We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.

@@

In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{lem susama} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$. In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.  Thus $q\in S_i$ and so $f$ is a factor of $r_i$.

Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e. that $I_{i-1}(q) = b$. Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$). This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{lem susama} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.

@@

Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{lem susama}. From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$. Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.

@@

First we show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.  Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$. There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\! \Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{lem susama}.  If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.  If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$. However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.  Thus $f$ divides $r_i$.

Next we need to show that $R$ is squarefree.  Suppose $f^2|R$.  If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.  This contradicts Lemma~\ref{lem susama}.  Now suppose $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.  \hlfix{Since $p$ comes before $q$ on edge $(a,b)$}{I can't figure out why this happens; what am I missing?} it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.  Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.  Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$. This is again a contradiction, and so $R$ is squarefree.

@@

To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{lem susama}.  By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and \hlfix{hence every factor of $R$ divides $R(W)$}{Is this obvious? Or does it follow from a previous result?}.  Finally, since $R$ is squarefree and monic, this implies that $R(W)$ is an integer multiple of $R$.
\end{proof}

>>>>

Note that if we take any admissible Wilson loop diagram and remove the unsupported vertices then we will obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
  %Then exactly one of the following two things occurs.
  %\begin{enumerate}
  %  \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
  %  \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
  %    \begin{enumerate}
  %      \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
  %      \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  %      \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
  %    \end{enumerate}
  %\end{enumerate}
\end{lem}

@@

\begin{rmk}
In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.  By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$.  Configuration \ref{item big and 2} necessarily entails vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.  So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
\end{rmk}

@@

Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.  The answer is that the set is a non-empty cyclic interval.  Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.

\begin{lem}\label{lem last vert}
  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.  Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
\end{lem}

@@

\textbf{case I}:  Suppose $p$ has one end on $(i-1, i)$.  Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap \interval{i+1}{b-1} = I_{i} \cap \interval{i+1}{b-1}$.  Furthermore, by Lemma~\ref{vertex cyclic int lem}, in building $I_{i+1}$, it must be that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.    Consequently, in building $I_{i+1}$, when at vertex $b$ no propagator still remaining is before $p$.  This is also true in building $I_i$ when at $b$ since the same propagators have been taken beforehand.  Additionally $k\geq_i b+1$.

@@

The first lemma is Lemma~\ref{vertex cyclic int lem} and I moved it up to a previous section.

@@

The third lemma is now lemma~\ref{lem sian}.

Here is some old text: Actually the result I need is not exactly Sian's result and what I will actually use is her proof.  Thus I will use notation and definitions (including length of a propagator and the specific $p_i$ and $q_i$ construction from the proof) from her note without further discussion.  The result I will actually use will be that in place of the hypothesis that $D$ has all vertices covered by at least two propagators I have that all vertices are covered by at least 1 propagator and there are no propagators of length 3.

@@

  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.  Thus $n-3\not\in I_1^{C}$ and so in building the Gra\ss mann necklace when we get to vertex $n-3$ any other covering propagators of $C$ have already been taken and so we can now take $p$.  Therefore $I_1^{D}= I_1^{C}\cup \{n-3\}$.

@@

  The remaining case is when $n-1,n-2\in I_{n-2}^{C}$ for the construction of $I_{n-2}^{D}$.  We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.  In the construction of $I_{n-2}^{D}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{C}$.  Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{C}$.  Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.  Thus we are proceeding like $I_{n}^{C}$ but without propagator $q$.  Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{C}$.  By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.  Therefore $I_{n-2}^{D} = (I_{n}^{C} - \{n-5\}) \cup \{n-1, n-2\}$.  This covers all cases and hence completes the proof.
\end{proof}

@@

  Also by Lemma~\ref{lem I} $I_{n-1}^{D} = I_n^{C} \cup \{n-1\}$.  Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.  Similarly $n-1, n-2\not\in I_n^{C}$.  Thus the paths putting the plusses in from $I_n^{C}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $D$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{D}$ contributes.  That is, we get all the plusses from $I_{n}^{C}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
\end{proof}

@@

\begin{proof}
  If $n-2\not\in I_{n-2}^{C}$ then $I_{n-1}^{C}=I_{n-2}^{C}$ and by Lemma~\ref{lem I} $I_{n-2}^{D} = I_{n-1}^{C} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{vertex cyclic int lem}.  Therefore the paths for $I_{n-2}^{D}$ are the paths for $I_{n-1}^{C}$ along with the $n-3\rightarrow n-2$ path.  This gives the statement of the lemma.

@@

\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.  
%Call the propagators which appear before $p$ is closed the propagators inside $p$. \note{It might be nice to have general language for this inside/outside idea.  What do you think.}

@@

\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.  Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$. We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.

@@

In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$. In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.  Thus $q\in S_i$ and so $f$ is a factor of $r_i$.

Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e. that $I_{i-1}(q) = b$. Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$). This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{vertex cyclic int lem} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.

@@

Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}. From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$. Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.

@@

First we show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.  Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$. There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\! \Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{vertex cyclic int lem}.  If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.  If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$. However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.  Thus $f$ divides $r_i$.

Next we need to show that $R$ is squarefree.  Suppose $f^2|R$.  If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.  This contradicts Lemma~\ref{vertex cyclic int lem}.  Now suppose $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.  \hlfix{Since $p$ comes before $q$ on edge $(a,b)$}{I can't figure out why this happens; what am I missing?} it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.  Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.  Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$. This is again a contradiction, and so $R$ is squarefree.

@@

To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.  By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and \hlfix{hence every factor of $R$ divides $R(W)$}{Is this obvious? Or does it follow from a previous result?}.  Finally, since $R$ is squarefree and monic, this implies that $R(W)$ is an integer multiple of $R$.
\end{proof}
